A Comparison of Graph Processing Systems

### 2020-09-19 documentation/paper/sections/overview/gemini.tex

Gemini is fairly lightweight and has a clearly defined API between the core framework and the implementations of the individual algorithms. The five already implemented algorithms are Single-Source Shortest-Path (SSSP), Breath-First Search (BFS), PageRank (PR), Connected-Components (CC) and Biconnected-Components (BC).

>>>>

Gemini is fairly lightweight and has a clearly defined API between the core framework and the implementations of the individual algorithms. The five already implemented algorithms are Single-Source Shortest-Path (SSSP), Breath-First Search (BFS), PageRank (PR), Connected-Components (CC) and Betweenness-Centrality (BC).

### 2020-09-19 documentation/paper/sections/preliminiaries.tex

\subsection{Push and Pull Variants}
Many parallel graph algorithms, as well as the three we consider here, are implemented by iterating over vertices, or edges \cite{tao}.
The respective vertex or edge, which is considered in an iteration, is also called \emph{active}.
Applying an operator to this \emph{active} vertex or edge is called an \emph{activity}.
This operator considers always only a local so called \emph{neighborhood} to the \emph{active} vertex or edge.
To this \emph{neighborhood} belong only vertices and edges, which are in the direct surrounding of the \emph{active} vertex or edge, which allows to parallelise the iteration relatively easy.

In general such an operator can change the whole structure of the \emph{neighbourhood}.
But in the following we assume, that an operator changes only \emph{labels} of vertices or edges in the \emph{neighbourhood}.
\emph{Labels} of edges also called \emph{weights}.
Often this operator can be implemented in two different ways, called \emph{push style} or \emph{pull style}.
A \emph{push-style} operator reads the \emph{label} of the \emph{active} vertex or edge and updates the \emph{label} of its \emph{neighborhood}.
In contrast the \emph{pull-style} operator reads all values of its \emph{neighborhood} and updates the value of the \emph{active} vertex or edge.

\emph{Pull-style} operators need less synchronization in parallel implementations, because unlike \emph{push style} there is only one write and many read operations. Thus locks can be avoided. So \emph{push-style} operators are more efficient, if there are only a few \emph{active} vertices or edges at the same time, or the \emph{neighborhoods} do not overlap, which can not be avoided in general. On the other hand \emph{pull-style} operators are more efficient, if there are many \emph{active} vertices or edges at the same time.

>>>>

\subsection{Push and Pull Variants}
Many parallel graph algorithms, as well as the three we consider here, are implemented by iterating over vertices \cite{tao}.
The respective vertex, which is considered in an iteration and the operator is applied to, is also called \emph{active}.
It's also possible to iterate over edges and consider them as \emph{active}, but in the following, whithout loss of generality, we will use the term \emph{active vertex}.
This operator considers always only a local so called \emph{neighborhood} to the \emph{active} vertex.
To this \emph{neighborhood} belong only vertices, which are in the direct surrounding of the \emph{active} vertex.
This allows to parallelise the iteration relatively easy, caused by the locality of the operator.

In general such an operator can change the whole structure of the \emph{neighbourhood}.
But in the following we assume, that an operator changes only \emph{labels} of vertices in the \emph{neighbourhood}.
\emph{Labels} of edges are also called \emph{weights}.
Often this operator can be implemented in two different ways, called \emph{push style} or \emph{pull style}.
A \emph{push-style} operator reads the \emph{label} of the \emph{active} vertex and updates the \emph{label} of its \emph{neighborhood}.
These operators are more efficient, if there are only a few \emph{active} vertices at the same time, or the \emph{neighborhoods} do not overlap, which can not be avoided in general.
In contrast the \emph{pull-style} operator reads all values of its \emph{neighborhood} and updates the value of the \emph{active} vertex.
\emph{Pull-style} operators need less synchronization in parallel implementations, because unlike \emph{push style} there is only one write and many read operations.
Thus locks can be avoided.
So these operators are more efficient, if there are many \emph{active} vertices at the same time.
